---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(width = 120)
```

# RcppUUID

<!-- badges: start -->

[![GitLab CI Build Status](https://gitlab.com/artemklevtsov/rcppuuid/badges/master/pipeline.svg)](https://gitlab.com/artemklevtsov/rcppuuid/-/pipelines)
[![AppVeyor Build status](https://ci.appveyor.com/api/projects/status/if9qot73i61ts59y?svg=true)](https://ci.appveyor.com/project/artemklevtsov/rcppuuid)
[![Codecov Code Coverage](https://codecov.io/gl/artemklevtsov/rcppuuid/branch/master/graph/badge.svg)](https://app.codecov.io/gl/artemklevtsov/rcppuuid)
[![CRAN Status](http://www.r-pkg.org/badges/version/RcppUUID)](https://cran.r-project.org/package=RcppUUID)
[![License: GPL v2](https://img.shields.io/badge/License-GPL%20v2-blue.svg)](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html)

<!-- badges: end -->

R package to generate Universally Unique Identifiers (UUIDs) version 4 and 5 using Boost C++ library.

## Installation

To install the package from the CRAN run the following command:

```{r, eval=FALSE}
install.packages("RcppUUID", repos = "https://cloud.r-project.org/")
```

Also you could install the dev-version with the `install_gitlab()` function from the `remotes` package:

```{r, eval=FALSE}
remotes::install_gitlab("artemklevtsov/rcppuuid")
```

This package contains the compiled code, therefore you have to use the [Rtools](https://cran.r-project.org/bin/windows/Rtools/) to install it on Windows.

## Usage

### Generate version 4 UUIDs

Generate single UUID:

```{r}
RcppUUID::uuid_generate_random()
```

Generate multiple UUIDs:

```{r}
RcppUUID::uuid_generate_random(5)
```

Check uniques for the uuids:

```{r}
unique_n <- function(x) length(unique(x))
n <- 1000000
unique_n(RcppUUID::uuid_generate_random(n)) == n
```

Benchmarking:

Single UUID:

```{r}
microbenchmark::microbenchmark(
  uuid = uuid::UUIDgenerate(FALSE),
  RcppUUID = RcppUUID::uuid_generate_random()
)
```

Multiple UUIDs:

```{r}
n <- 10000
microbenchmark::microbenchmark(
  uuid = uuid::UUIDgenerate(FALSE, n),
  RcppUUID = RcppUUID::uuid_generate_random(n)
)
```

### Generate version 5 UUIDs

Generate version UUIDs based on the text input:

```{r}
RcppUUID::uuid_generate_name(letters[1:5])
```

For the each unique input will be generated unique UUID. Check uniqueness:

```{r}
uuids <- replicate(10, RcppUUID::uuid_generate_name(letters))
length(unique(as.vector(uuids))) == length(letters)
```

### Validate UUIDs

```{r}
RcppUUID::uuid_validate(NA_character_)
RcppUUID::uuid_validate("")
RcppUUID::uuid_validate("not uuid")
RcppUUID::uuid_validate(RcppUUID::uuid_generate_random(5))
RcppUUID::uuid_validate(RcppUUID::uuid_generate_nil(5))
RcppUUID::uuid_validate(RcppUUID::uuid_generate_name(letters[1:5]))
```


## Bug reports

Use the following command to go to the page for bug report submissions:

```{r, eval=FALSE}
bug.report(package = "RcppUUID")
```

Before reporting a bug or submitting an issue, please do the following:

- Make sure that you error or issue was not reported or discussed earlier. Please, use the search;
- Check the news list of the current version. Some errors could be caused by the package changes. It could be done with `news(package = "RcppUUID", Version == packageVersion("RcppUUID"))` command;
- Make a minimal reproducible example of the code that consistently causes the error;
- Make sure that the error occurs during the execution of a function from the `RcppUUID` package, not from other packages;
- Try to reproduce the error with the last development version of the package from the git repository.

Please attach traceback() and sessionInfo() output to bug report. It may save a lot of time.

## License

The `RcppUUID` package is distributed under [GPLv2](http://www.gnu.org/licenses/gpl-2.0.html) license.
